The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-01-20 SC-challenge-arxiv.tex
fixed author list in arXiv version

\author{
Kyle E.\ Niemeyer\\
School of Mechanical, Industrial, and Manufacturing Engineering,\\
Oregon State University\\
\href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}
\and
Daniel S. Katz\\
Computation Institute, University of Chicago \&\\
Argonne National Laboratory\\
\href{mailto:d.katz@ieee.org}{d.katz@ieee.org}
\and
Arfon M. Smith\\
GitHub Inc.\\
\href{mailto:arfon@github.com}{arfon@github.com}
}

>>>>

\author{
Kyle E.\ Niemeyer\\
School of Mechanical, Industrial, and Manufacturing Engineering,\\
Oregon State University\\
\href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}
\and
Arfon M.\ Smith\\
GitHub Inc.\\
\href{mailto:arfon@github.com}{arfon@github.com}
\and
Daniel S.\ Katz\\
Computation Institute, University of Chicago \&\\
Argonne National Laboratory\\
\href{mailto:d.katz@ieee.org}{d.katz@ieee.org}
}
